---
title: "Government Type Analysis"
author: "Joe Margolis"
date: '2022-11-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(survival)
library(readr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(ggmap)
library(dplyr)
library(rvest)
library(stringr)
library(kableExtra)
```

```{r}
load("GovGDP.csv")
```

```{r}
Gov0 <- GovGDP %>%
  filter(regime_bmr_owid == 0 | regime_bmr_owid == 4)
Gov1 <- GovGDP %>%
  filter(regime_bmr_owid == 1 | regime_bmr_owid ==3)
```

```{r}
Govkm0 = survfit( Surv(doublingTime, (status)) ~ 1, conf.type = 'plain',  data = Gov0  )
Govkm1 = survfit( Surv(doublingTime, (status)) ~ 1, conf.type = 'plain', data = Gov1   )

plot(Govkm0, conf.int = FALSE, xlab = "Years", ylab = "GDP Doubling Time Probability", main = "GDP Doubling Times of Democracies vs. Non-Democracies")
lines(Govkm1, conf.int = FALSE, col = "red")
legend(1,0.2,c("Non-Democracy","Democracy"),col=c("black","red") , text.col=c("black","red") , lty=1 , cex=0.8 )
```

## Non-Democracy Model Fitting

```{r}
NDNorm <- survreg( Surv(doublingTime, status) ~ 1, data = Gov0, dist = "gaussian"   )
NDWeib <- survreg( Surv(doublingTime, status) ~ 1, data = Gov0, dist = "weibull"   )
NDExp <- survreg( Surv(doublingTime, status) ~ 1, data = Gov0, dist = "exponential"   )
survreg( Surv(doublingTime, status) ~ 1, data = Gov0, dist = "lognormal"   )

summary(NDWeib)
```

```{r}

mean = 34.45879 
sd = 22.15558   

NoDemNorm = function(x) {
  
  1-pnorm(x, mean = mean, sd = sd)
}

plot(Govkm0, conf.int = FALSE)

curve(NoDemNorm, add = TRUE, col = "red")


scale = exp(3.78953)
shape = 1/ 0.8044466

NoDemWeib = function(x) {
  
  1-pweibull(x, shape= shape, scale = scale)
}

curve(NoDemWeib, add = TRUE, col = "blue")

rate = 1/exp(3.888212)

NoDemExp = function(x) {
  
  1-pexp(x, rate = rate)
}

curve(NoDemExp, add = TRUE, col = "green")

mean = 3.436134 
sd = 1.066429    

NoDemLN = function(x) {
  
  1-plnorm(x, mean = mean, sd = sd)
}

curve(NoDemLN, add = TRUE, col = "purple")
```
Cox Snells For Each

```{r}
CoxSnellWeib = function(cs,status,xlim=NULL,ylim=NULL)
{
kmcs = survfit( Surv(jitter(cs,amount=(max(cs)-min(cs))/1000),status) ~ 1 )$surv

plot( log(-log(kmcs)) ~ sort(log(cs)) ,
      xlab="log(Cox-Snell)", ylab="log(-log(S(Cox-Snell)))", main = "Weibull Cox-Snell Residuals", xlim=xlim, ylim=ylim )

abline(0,1,col='red')
}

CoxSnellLN = function(cs,status,xlim=NULL,ylim=NULL)
{
kmcs = survfit( Surv(jitter(cs,amount=(max(cs)-min(cs))/1000),status) ~ 1 )$surv

plot( log(-log(kmcs)) ~ sort(log(cs)) ,
      xlab="log(Cox-Snell)", ylab="log(-log(S(Cox-Snell)))", main = "Log-Normal Cox-Snell Residuals", xlim=xlim, ylim=ylim )

abline(0,1,col='red')
}
```

Exponential Cox Snell

```{r}
CoxSnell = function(cs,status,xlim=NULL,ylim=NULL)
{
kmcs = survfit( Surv(jitter(cs,amount=(max(cs)-min(cs))/1000),status) ~ 1 )$surv

plot( log(-log(kmcs)) ~ sort(log(cs)) ,
      xlab="log(Cox-Snell)", ylab="log(-log(S(Cox-Snell)))", xlim=xlim, ylim=ylim )

abline(0,1,col='red')
}

CSExp <- -log( 1 - pexp( Gov0$doublingTime , 1/exp(3.888212) ) )

CoxSnell( CSExp , Gov0$status )
```


Weibull Cox Snell

```{r}
CSWeib <- -log( 1 - pweibull( Gov0$doublingTime , 1/0.8044466, exp(3.78953) ) )

CoxSnellWeib( CSWeib , Gov0$status )
```
Log-Normal Cox Snell

```{r}
CSLN <- -log( 1 - plnorm( Gov0$doublingTime , 3.436134, 1.066429 ) )

CoxSnellLN( CSLN , Gov0$status )
```

```{r}
CSNorm <- -log( 1 - pnorm( Gov0$doublingTime , 34.45879 , 22.15558 ) )

CoxSnell( CSNorm , Gov0$status )
```

```{r}
CSExp <- -log( 1 - pexp( Gov0$doublingTime ,1/exp(3.888212) ) )

CoxSnell( CSExp , Gov0$status )
```

#### LRT Between exponential and weibull

```{r}
NDExp$loglik
NDWeib$loglik
```


Log Normal testing

```{r}
m1 <- survreg( Surv(doublingTime, status) ~ 1, data = Gov0, dist = "lognormal"   )
m2 <- survreg( Surv(doublingTime, status) ~ Threshold, data = Gov0, dist = "lognormal"   )

m1$loglik
m2$loglik

testStat <- (2*-158.6001) - (2*-162.1257)
1-pchisq(testStat, 1)
```

Threshold is also statistically significant 

```{r}
m3 <- survreg( Surv(doublingTime, status) ~ Threshold + yearsSince1960, data = Gov0, dist = "lognormal"   )

m2$loglik
m3$loglik

testStat <- (2*-158.0051) - (2*-158.6001)
1-pchisq(testStat, 1)
```

Years since 1960 not statistically significant

```{r}
m4 <- survreg( Surv(doublingTime, status) ~ Threshold + EnergyUse, data = Gov0, dist = "lognormal"   )

m2$loglik
m4$loglik

testStat <- (2*-111.6340) - (2*-158.6001)
1-pchisq(testStat, 1)
```

Energy use is statistically significant

```{r}
m5 <- survreg( Surv(doublingTime, status) ~ Threshold + EnergyUse + SecondaryEnrollment, data = Gov0, dist = "lognormal"   )
```

```{r}
m4$loglik
m5$loglik

testStat <- (2*-63.68472) - (2*-111.6340)
1-pchisq(testStat, 1)
```
Secondary school enrollment is statistically significant

```{r}
summary(m5)
```


## Democracy Fitting

```{r}
survreg( Surv(doublingTime, status) ~ 1, data = Gov1, dist = "gaussian"   )
survreg( Surv(doublingTime,status) ~ 1, data = Gov1, dist = "weibull"   )
survreg( Surv(doublingTime, status) ~ 1, data = Gov1, dist = "exponential"   )
survreg( Surv(doublingTime, status) ~ 1, data = Gov1, dist = "lognormal"   )
```

```{r}

mean = 29.80413 
sd = 13.1161   

DemNorm = function(x) {
  
  1-pnorm(x, mean = mean, sd = sd)
}

plot(Govkm1)

curve(DemNorm, add = TRUE, col = "red")


scale = exp(3.535108)
shape = 1/ 0.441614

DemWeib = function(x) {
  
  1-pweibull(x, shape= shape, scale = scale)
}

curve(DemWeib, add = TRUE, col = "blue")

rate = 1/exp(3.773645)

DemExp = function(x) {
  
  1-pexp(x, rate = rate)
}

curve(DemExp, add = TRUE, col = "green")

mean = 3.306469 
sd = 0.552448    

DemLN = function(x) {
  
  1-plnorm(x, mean = mean, sd = sd)
}

curve(DemLN, add = TRUE, col = "purple")
```

```{r}
curve(1-plnorm(x, mean = 3.306469, sd = 0.552448), ylab = "Survival", xlab = "Years")
curve( 1-plnorm(x, mean = 3.436134, sd = 1.066429), add = TRUE, col = "gold")
```


Exponential Dem Cox Snell

```{r}
CSExp <- -log( 1 - pexp( Gov1$doublingTime , 1/exp(3.773645) ) )

CoxSnell( CSExp , Gov1$status )
```

Weibull Dem Cox Snell

```{r}
CSWeib <- -log( 1 - pweibull( Gov1$doublingTime , 1/0.441614, exp(3.535108) ) )

CoxSnellWeib( CSWeib , Gov1$status )
```

Dem Normal CS

```{r}
CSNorm <- -log( 1 - pnorm( Gov1$doublingTime , 29.80413 , 13.1161) )

CoxSnell( CSNorm , Gov1$status )
```

Dem Log Normal CS

```{r}
CSLN <- -log( 1 - plnorm( Gov1$doublingTime , 3.306469, 0.552448) )

CoxSnellLN( CSLN , Gov1$status )
```

#### Log Normal Covariates Testing Democracy

```{r}
m1 <- survreg( Surv(doublingTime, status) ~ 1, data = Gov1, dist = "lognormal"   )
m2 <- survreg( Surv(doublingTime, status) ~ Threshold, data = Gov1, dist = "lognormal"   )

m1$loglik
m2$loglik

testStat <- (2*-218.3843) - (2*-222.8125)
1-pchisq(testStat, 1)
```

Threshold has statistical significance

```{r}
m3 <- survreg( Surv(doublingTime, status) ~ Threshold + yearsSince1960, data = Gov1, dist = "lognormal"   )

m2$loglik
m3$loglik

testStat <- (2*-218.1054) - (2*-218.3843)
1-pchisq(testStat, 1)
```
years since 1960 does not add statistical significance

```{r}
m4 <- survreg( Surv(doublingTime, status) ~ Threshold + EnergyUse, data = Gov1, dist = "lognormal"   )

m2$loglik
m4$loglik

testStat <- (2*-149.7570) - (2*-218.3843)
1-pchisq(testStat, 1)
```

Including Energy Use also has statistical significance

```{r}
m5 <- survreg( Surv(doublingTime, status) ~ Threshold + EnergyUse + SecondaryEnrollment, data = Gov1, dist = "lognormal"   )
```

```{r}
m4$loglik
m5$loglik

testStat <- (2*-96.69909) - (2*-149.7570)
1-pchisq(testStat, 1)
```
Secondary school enrollment is statistically significant

```{r}
summary(m5)
```
```{r}
AllMod <- survreg( Surv(doublingTime, status) ~ factor(regime_bmr_owid) + EnergyUse + SecondaryEnrollment, data = GovGDP, dist = "lognormal"   )

AllMod

HDem <- function(x) dlnorm(x,4.281254e+00-2.700882e-01 + (0.0001587215 * mean(GovGDP$EnergyUse)) - (0.0081907981 * mean(GovGDP$SecondaryEnrollment)),  0.395  )/(1-plnorm(x,4.281254e+00-2.700882e-01 + (0.0001587215 * mean(GovGDP$EnergyUse)) - (0.0081907981 * mean(GovGDP$SecondaryEnrollment)),  0.395 ))


HNoDem <- function(x) dlnorm(x,4.281254e+00 + (0.0001587215 * mean(GovGDP$EnergyUse)) - (0.0081907981 * mean(GovGDP$SecondaryEnrollment)),  0.395  )/(1-plnorm(x,4.281254e+00 + (0.0001587215 * mean(GovGDP$EnergyUse)) - (0.0081907981 * mean(GovGDP$SecondaryEnrollment)),  0.395 ))
```
```{r}
curve( HDem , ylim = c(0,1), ylab="Hazard" )

curve( HNoDem , add=TRUE , lty=2 )
```

### Doig Covariates on full model

```{r}
m1 <- survreg( Surv(doublingTime, status) ~ factor(regime_bmr_owid) , data = GovGDP, dist = "lognormal"   )

summary(m1)
```

### Using Democracy vs. Non Democracy as a Time Variables

```{r}
coxMod <- coxph(Surv(doublingTime, status) ~ factor(regime_bmr_owid) , data = GovGDP)
coxMod
schoen <- cox.zph(coxMod)
plot(schoen, ylab = "Beta(t) For Democracy vs. Non-Democracy", xlab = "Years", main = "Schoenfeld Residuals With only Demcracy Status")
abline(a= 0.1361, b = 0, add=TRUE, col = "red")
abline(a= 0, b = 0, add=TRUE, col = "green")
abline(a= 0.1361, b = 0, add=TRUE, col = "red")

p <- locator()
abline(v=p$x, lty=3)

```
```{r}
coxMod <- coxph(Surv(doublingTime, status) ~ factor(regime_bmr_owid) + strata(Threshold) , data = GovGDP)
coxMod
schoen <- cox.zph(coxMod)
plot(schoen, ylab = "Beta(t) for Democracy vs. Non-Democracy", xlab = "Years", main = "Schoenfeld Residuals For Demcracy Status Stratified by Threshold")
abline(a= 0.2913, b = 0, add=TRUE, col = "red")
abline(a= 0, b = 0, add=TRUE, col = "green")

```
```{r}
survreg(Surv(doublingTime, status) ~1 , data = Gov0, dist = "lognormal"  )
survreg(Surv(doublingTime, status) ~1 , data = Gov0, dist = "weibull"  )

```
```{r}
survreg(Surv(doublingTime, status) ~1 , data = Gov1, dist = "lognormal"  )
survreg(Surv(doublingTime, status) ~1 , data = Gov1, dist = "weibull"  )
```

```{r}
write.csv(GovGDP, "NewGovGDP.csv")
```

```{r}
GovGDPTVC<- read.csv("NewGovGDPTVC.csv") 

GovGDPTVC <- GovGDPTVC[!is.na(GovGDPTVC$regime_bmr_owid), ] 

GovGDPTVC <- GovGDPTVC %>%
  filter(regime_bmr_owid == 1 | regime_bmr_owid == 0)
```

```{r}
coxModTVC <- coxph(Surv(start, stop, status.time) ~ factor(regime_bmr_owid) + factor(regime_bmr_owid)*stop , data = GovGDPTVC)
coxModTVC
schoenTVC <- cox.zph(coxModTVC)
plot(schoenTVC, ylab = "Beta(t) For Democracy vs. Non-Democracy", xlab = "Years", main = "Schoenfeld Residuals With only Demcracy Status With TVC")
abline(a= -1.53685, b = 0.08400, add=TRUE, col = "red")
```

```{r}
`Time Varying Representation` <- c("regime_bmr_owid = 1", "regime_bmr_owid = 1:Stop")
Coefficient <- c(-1.53685, 0.08400)
`Exponentiated Coefficient` <- c(0.21506, 1.08763)
`P-Value` <- c(0.002929,0.000562)

TVC <- data.frame(`Time Varying Representation`, Coefficient, `Exponentiated Coefficient`, `P-Value` )

TVC %>%
  kbl(caption = "Time Varying Coefficients of Cox-PH Model", col.names = c("Time Varying Representation", "Coefficient", "Exponentiated Coefficient", "P-Value")) %>%
  kable_classic_2()
```


```{r}
coxModTVCFull <- coxph(Surv(start, stop, status.time) ~ factor(regime_bmr_owid) + factor(regime_bmr_owid)*stop  + strata(Threshold) , data = GovGDPTVC)
coxModTVCFull
schoenTVCFull <- cox.zph(coxModTVCFull)
plot(schoenTVCFull, ylab = "Beta(t) for Democracy vs. Non-Democracy", xlab = "Years", main = "Schoenfeld Residuals For Demcracy Status Stratified by Threshold")
abline(a= -1.39743, b = 0.09397, add=TRUE, col = "red")
```

```{r}
`Time Varying Representation` <- c("regime_bmr_owid = 1", "regime_bmr_owid = 1:Stop")
Coefficient <- c(-1.39743, 0.09397)
`Exponentiated Coefficient` <- c(0.24723, 1.09853)
`P-Value` <- c(0.02247,0.00336)

StratifiedTVC <- data.frame(`Time Varying Representation`, Coefficient, `Exponentiated Coefficient`, `P-Value` )

StratifiedTVC %>%
  kbl(caption = "Time Varying Coefficients of Cox-PH Model Stratified by Threshold", col.names = c("Time Varying Representation", "Coefficient", "Exponentiated Coefficient", "P-Value")) %>%
  kable_classic_2()
```

